Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-06-22 Report/simulation_intro.tex
updated nam comments review should be modified
updated

The simulations carried out in this work consider the \ac{PL} varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples. The queues are generated based on the Poisson process with the average values specified in each section presented. 
\begin{table*}
	\centering
	\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
	\renewcommand{\arraystretch}{1.25} \scriptsize
	\begin{tabular}{|*{14}{c|}}
		\hline
		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
		\cline{3-14}
		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
		\hline
		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
		\hline
		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
		\hline
	\end{tabular}
	\label{tbl-1}
\end{table*}
\begin{figure*}
	\centering
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-1-4}
		\label{fig-1}}
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-2-5}
		\label{fig-2}}
	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates \review{using \me{\ell_1 (q = 1)} norm for \ac{JSFRA} schemes}}
	\label{fig-a}
\end{figure*}

>>>>

The simulations carried out in this work consider the \ac{PL} varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples. The queues are generated based on the Poisson process with the average values specified in each section presented. 
\begin{table*}
	\centering
	\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
	\renewcommand{\arraystretch}{1.25} \scriptsize
	\begin{tabular}{|*{14}{c|}}
		\hline
		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \emph{backpressure})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
		\cline{3-14}
		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
		\hline
		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
		\hline
		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
		\hline
	\end{tabular}
	\label{tbl-1}
\end{table*}
\begin{figure*}
	\centering
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-1-4}
		\label{fig-1}}
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-2-5}
		\label{fig-2}}
	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates using \me{\ell_1 (q = 1)} norm for \ac{JSFRA} schemes}
	\label{fig-a}
\end{figure*}

### 2015-06-22 Report/simulation_results.tex
updated

For a \ac{MIMO} scenario, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the associations are made by selecting the \ac{BS} with the lowest \ac{PL} component. Fig. \subref*{fig-1} shows the performance of the centralized schemes for a single receive antenna system. The total number of queued packets for Fig. \subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-3-2}
	\caption{Convergence of the centralized and the distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace} \review{using \me{\ell_1} norm for \ac{JSFRA} schemes}}
	\label{fig-d}
\end{figure}

>>>>

For a \ac{MIMO} scenario, we consider a system with \review{\me{N=4,2}} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the associations are made by selecting the \ac{BS} with the lowest \ac{PL} component. Fig. \subref*{fig-1} shows the performance of the centralized schemes for a single receive antenna system. The total number of queued packets for Fig. \subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-3-2}
	\caption{Convergence of the centralized and the distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace} using \me{\ell_1} norm for \ac{JSFRA} schemes}
	\label{fig-d}
\end{figure}

### 2015-06-22 Report/sub_channel_wsrm.tex
updated - final - draft
updated

The complexity of the \ac{JSFRA} algorithm scales quickly with the number of sub-channels, since the complexity of the interior point method, which is used to solve the problem, increases quickly with the problem size. Thus, we can use the decomposition methods presented in \cite{palomar2006tutorial,boyd2011distributed} to overcome this complexity by designing precoders for each sub-channels independently with minimal information exchange.

As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}. The sharing of power can be equal or based on a predetermined pattern as in partial frequency reuse for the sub-channels as given by
\begin{equation}
\sum_{i=1}^N P_{\max,i} = P_{\max}.
\end{equation}
Even though \me{N} sub-channels are present at any given scheduling instant, precoders are computed for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the number of backlogged packets. Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} before solving for the precoders specific to the sub-channel \me{i}. Since the precoder design is sequential, \textit{i.e}, the precoders are designed for sub-channels \me{[0,i-1]} before \me{\ith{i}} sub-channel, the number of backlogged packets for the initial sub-channel is initialized as \me{Q_{k,1} = Q_k}. The queues associated with the consecutive sub-channels are given by
\begin{equation}	\label{eqn-weight}
	Q_{k,i+1} = \max \Big ( Q_k - \sum_{j = 1}^{i} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big ) \; \forall \; k \in \mathcal{U}
\end{equation}
where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream. Note that the proposed scheme is sensitive to the order of the sub-channel selection due to the sequential precoder design for each sub-channel. However, the \ac{SRA} approach provides faster convergence in contrast to the \ac{JSFRA} formulation due to the substantial reduction in the optimization variables for each sub-channel problem. As the number of users in the system increases, the \ac{SRA} formulation will be insensitive to the sub-channel ordering due to the multi-user diversity.
%The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
%\begin{algorithm}
% \SetAlgoLined
% \DontPrintSemicolon
% \BlankLine
% \SetKwInput{KwInit}{Initialize}
% \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
% \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
% \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
% update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}\;
% \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
% \KwInit{\me{i=0} and \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
% update \me{\mvec{w}{l,k,\hat{n}}} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} using \eqref{eqn-10} and \eqref{eqn-8}\;
% \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
% initialize \me{j = 0}\;
% \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
% solve for \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}}\;
% update the constraint set \eqref{eqn-8} with \me{\tilde{u}_{l,k,\hat{n}}} and \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr}\;
% $j = j + 1$\;
% }
% update \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
% $i = i + 1$\;
% }
% }
% \caption{Algorithm of \acs{SRA} scheme}
% \label{algo-5}
%\end{algorithm}
%

>>>>

The complexity of the \ac{JSFRA} algorithm scales quickly with the number of sub-channels, since the complexity of the interior point method, which is used to solve the problem, increases with the problem size. Thus, we can use the decomposition methods presented in \cite{palomar2006tutorial,boyd2011distributed} to overcome this complexity by designing precoders for each sub-channels independently with minimal information exchange.

As an alternative sub-optimal solution, we present a \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}. The sharing of power can be equal or based on a predetermined pattern as in partial frequency reuse for the sub-channels as given by
\begin{equation}
\sum_{i=1}^N P_{\max,i} = P_{\max}.
\end{equation}
Even though \me{N} sub-channels are present at any given scheduling instant, precoders are computed for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the number of backlogged packets. Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} before solving for the precoders specific to the sub-channel \me{i}. Since the precoder design is sequential, \textit{i.e}, the precoders are designed for sub-channels \me{[0,i-1]} before \me{\ith{i}} sub-channel, the number of backlogged packets for the initial sub-channel is initialized as \me{Q_{k,1} = Q_k}. The queues associated with the consecutive sub-channels are given by
\begin{equation}	\label{eqn-weight}
	Q_{k,i+1} = \max \Big ( Q_k - \sum_{j = 1}^{i} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big ) \; \forall \; k \in \mathcal{U}
\end{equation}
where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream. \review{Inspite of the improved covergence speed over the \ac{JSFRA} approach, the \ac{SRA} scheme is sensitive to the order in which the sub-channels are selected. Heuristically, we can adopt \ac{MU}-\ac{MIMO} scheduling scheme in \cite{sus2006zfbf} to find an efficient subset of users and the corresponding sum rate using zero-forcing precoders in each sub-channel, which can be used to determine the selection order. Since the scheduling is based on the infinite buffer model, it is used only in the sub-channel ordering. However, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the multi-user diversity.}

%The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
%\begin{algorithm}
% \SetAlgoLined
% \DontPrintSemicolon
% \BlankLine
% \SetKwInput{KwInit}{Initialize}
% \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
% \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
% \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
% update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}\;
% \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
% \KwInit{\me{i=0} and \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
% update \me{\mvec{w}{l,k,\hat{n}}} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} using \eqref{eqn-10} and \eqref{eqn-8}\;
% \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
% initialize \me{j = 0}\;
% \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
% solve for \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}}\;
% update the constraint set \eqref{eqn-8} with \me{\tilde{u}_{l,k,\hat{n}}} and \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr}\;
% $j = j + 1$\;
% }
% update \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
% $i = i + 1$\;
% }
% }
% \caption{Algorithm of \acs{SRA} scheme}
% \label{algo-5}
%\end{algorithm}
%

### 2015-06-22 Report/system_model.tex
updated

We adopt linear transmit beamforming technique at \acp{BS}. Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted. In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user. Consequently, the received data estimate corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
\iftoggle{single_column}{
\begin{equation}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
\end{equation}
}{
\begin{multline}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n} \\ 
+ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
\end{multline}
}
where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream. In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams.\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users. \me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted.} Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{\enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}
\end{equation}
where \me{\enoise = N_0 \, \trace (\mvec{w}{l,k,n} \mbf{w}_{l,k,n}^\herm)} denotes the equivalent noise variance. \review{To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system in which \acp{BS} can estimate the downlink channels from the uplink pilots using channel reciprocity.}

>>>>

We adopt linear transmit beamforming technique at \acp{BS}. Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted. In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user. Consequently, the received data estimate corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
\iftoggle{single_column}{
\begin{equation}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
\end{equation}
}{
\begin{multline}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n} \\ 
+ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
\end{multline}
}
where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream. In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams.\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users. \me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted.} Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{\enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}
\end{equation}
where \me{\enoise = N_0 \, \trace (\mvec{w}{l,k,n} \mbf{w}_{l,k,n}^\herm)} denotes the equivalent noise variance. To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system in which \acp{BS} can estimate the downlink channels from the uplink pilots using channel reciprocity.
